---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---


```{r}
library(conflicted)
library(here)
library(tidyverse)
library(kableExtra)

conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
```


```{r}
########### Analyse Simulation: compare p-values to 0.01 and 0.05 cut-offs

sum_list <- list()
sum_rej_05_list <- list()
sum_rej_01_list <- list()

load(here("data-raw","simulations","spec_list.RData"))
spec_n <- NROW(specs)

missing <- 0

for (l in 1:spec_n){
  
  # l <- 1
  # res <- list.res[[l]]
  if(file.exists(here("data-raw","simulations",paste0(paste0(specs[l,],collapse = "_"),".RData")))){
    load(here("data-raw","simulations",paste0(paste0(specs[l,],collapse = "_"),".RData")))
  } else{
    print(paste0("File Specification ",l," skipped - not found."))
    missing <- missing + 1
    next
  }
  
  
  res.rej05 <- res[,2:NCOL(res)]
  res.rej05$rej <- NA
  res.rej05$rej.L2.boot <- NA
  res.rej05$rej.L1.boot <- NA
  res.rej05$rej.dist.boot <- NA
  
  res.rej05$rej.prop.test <- NA
  res.rej05$rej.prop.test.boot <- NA
  res.rej05$rej.prop.boot <- NA
  
  
  
  res.rej05$rej[res.rej05$is.dist1.p > 0.05] <- 999
  res.rej05$rej[res.rej05$is.dist1.p < 0.05] <- 1
  res.rej05$rej[res.rej05$rej > 1] <- 0
  
  res.rej05$rej.L2.boot[res.rej05$is.dist1.boot.L2.p > 0.05] <- 999
  res.rej05$rej.L2.boot[res.rej05$is.dist1.boot.L2.p < 0.05] <- 1
  res.rej05$rej.L2.boot[res.rej05$rej.L2.boot > 1] <- 0
  
  res.rej05$rej.L1.boot[res.rej05$is.dist1.boot.L1.p > 0.05] <- 999
  res.rej05$rej.L1.boot[res.rej05$is.dist1.boot.L1.p < 0.05] <- 1
  res.rej05$rej.L1.boot[res.rej05$rej.L1.boot > 1] <- 0
  
  res.rej05$rej.dist.boot[res.rej05$is.dist1.boot.dist.p > 0.05] <- 999
  res.rej05$rej.dist.boot[res.rej05$is.dist1.boot.dist.p < 0.05] <- 1
  res.rej05$rej.dist.boot[res.rej05$rej.dist.boot > 1] <- 0
  
  
  ####proportion test
  res.rej05$rej.prop.test[res.rej05$is.prop.test.p > 0.05] <- 999
  res.rej05$rej.prop.test[res.rej05$is.prop.test.p < 0.05] <- 1
  res.rej05$rej.prop.test[res.rej05$rej.prop.test > 1] <- 0
  
  res.rej05$rej.prop.test.boot[res.rej05$is.prop.boot.test.p > 0.05] <- 999
  res.rej05$rej.prop.test.boot[res.rej05$is.prop.boot.test.p < 0.05] <- 1
  res.rej05$rej.prop.test.boot[res.rej05$rej.prop.test.boot > 1] <- 0
  
  res.rej05$rej.prop.boot[res.rej05$is.prop.boot.p > 0.05] <- 999
  res.rej05$rej.prop.boot[res.rej05$is.prop.boot.p < 0.05] <- 1
  res.rej05$rej.prop.boot[res.rej05$rej.prop.boot > 1] <- 0
  
  
  
  
  
  res.rej05$id <- res$id
  res.rej05$id.seq <- res$id.seq
  
  
  sum_rej_05_list[[l]] <- colMeans(res.rej05, na.rm = TRUE)
  
  
  res.rej01 <- res[,2:NCOL(res)]
  res.rej01$rej <- NA
  res.rej01$rej.L2.boot <- NA
  res.rej01$rej.L1.boot <- NA
  res.rej01$rej.dist.boot <- NA
  
  res.rej01$rej.prop.test <- NA
  res.rej01$rej.prop.test.boot <- NA
  res.rej01$rej.prop.boot <- NA
  
  
  
  res.rej01$rej[res.rej01$is.dist1.p > 0.01] <- 999
  res.rej01$rej[res.rej01$is.dist1.p < 0.01] <- 1
  res.rej01$rej[res.rej01$rej > 1] <- 0
  
  res.rej01$rej.L2.boot[res.rej01$is.dist1.boot.L2.p > 0.01] <- 999
  res.rej01$rej.L2.boot[res.rej01$is.dist1.boot.L2.p < 0.01] <- 1
  res.rej01$rej.L2.boot[res.rej01$rej.L2.boot > 1] <- 0
  
  res.rej01$rej.L1.boot[res.rej01$is.dist1.boot.L1.p > 0.01] <- 999
  res.rej01$rej.L1.boot[res.rej01$is.dist1.boot.L1.p < 0.01] <- 1
  res.rej01$rej.L1.boot[res.rej01$rej.L1.boot > 1] <- 0
  
  res.rej01$rej.dist.boot[res.rej01$is.dist1.boot.dist.p > 0.01] <- 999
  res.rej01$rej.dist.boot[res.rej01$is.dist1.boot.dist.p < 0.01] <- 1
  res.rej01$rej.dist.boot[res.rej01$rej.dist.boot > 1] <- 0
  
  ###proportion test
  res.rej01$rej.prop.test[res.rej01$is.prop.test.p > 0.01] <- 999
  res.rej01$rej.prop.test[res.rej01$is.prop.test.p < 0.01] <- 1
  res.rej01$rej.prop.test[res.rej01$rej.prop.test > 1] <- 0
  
  res.rej01$rej.prop.test.boot[res.rej01$is.prop.boot.test.p > 0.01] <- 999
  res.rej01$rej.prop.test.boot[res.rej01$is.prop.boot.test.p < 0.01] <- 1
  res.rej01$rej.prop.test.boot[res.rej01$rej.prop.test.boot > 1] <- 0
  
  res.rej01$rej.prop.boot[res.rej01$is.prop.boot.p > 0.01] <- 999
  res.rej01$rej.prop.boot[res.rej01$is.prop.boot.p < 0.01] <- 1
  res.rej01$rej.prop.boot[res.rej01$rej.prop.boot > 1] <- 0
  
  
  
  
  
  res.rej01$id <- res$id
  res.rej01$id.seq <- res$id.seq
  
  sum_rej_01_list[[l]] <- colMeans(res.rej01, na.rm = TRUE)
  
  
}

print(paste0("Number of files still missing: ",missing))


sum.05 <- do.call(rbind.data.frame, sum_rej_05_list)
names(sum.05) <- names(sum_rej_05_list[[401]])
sum.05$test.lev <- 0.05

sum.01 <- do.call(rbind.data.frame, sum_rej_01_list)
names(sum.01) <- names(sum_rej_01_list[[401]])
sum.01$test.lev <- 0.01

###combine
sum.01.m <- merge(sum.01, specs, by="id")
sum.05.m <- merge(sum.05, specs, by="id")

sum_tab <- rbind(sum.01.m, sum.05.m)
```


```{r}
sum_tab
```


```{r}
plot_specs_overall <- dplyr::distinct(specs,hypothesis,out_prop, bootstrap, dist, ar, p_alpha, nreg, lambda)
```


```{r}
table_change <- function(input_table, caption, label){
  # insert caption
  tab <- gsub("\\begin{table}",
              paste0("\\begin{table}
                   \\caption{",caption,"}
                   \\label{",label,"}"), input_table, fixed = TRUE)
  
  # fixing the header
  # tab <- gsub("\\begin{tabular}",
  #             "\\resizebox{\\textwidth}{!}{\\begin{tabular}",tab, fixed = TRUE)
  # 
  # # fixiing the footer
  # tab <- gsub("\\end{tabular}",
  #             "\\end{tabular}}",tab, fixed = TRUE)
  
  return(tab)
}
```


```{r}
remove_tabletex <- function(table){
  gsub("\\end{table}","",gsub("\\begin{table}","",table, fixed = TRUE), fixed = TRUE)
}


column_tables <- function(table_list, tex_alone = FALSE, caption = "", label = "", resize = FALSE){
  
  cols = length(table_list)
  
  colwidth = round((1/cols),2)-0.01
  
  
  tab_intermed <- paste0("\\begin{table}\n\\small")
  
  tab_intermed <- paste0(tab_intermed, 
                         "\n\\caption{",caption,"}", 
                         "\n\\label{",label,"}")
  
  
  for(i in 1:cols){
    paste0(tab_intermed,
           "\n \\parbox{",colwidth,"\\textwidth}{",
           ifelse(resize, paste0("\\resizebox{",colwidth,"\\textwidth}{!}{"),""),
           remove_tabletex(table_list[[i]]), 
           ifelse(resize,"}}","}"), 
           ifelse(test = i != cols, 
                  yes = paste0("\n \\hfill"),
                  no = "\n \\end{table}")
    ) -> tab_intermed
  }
  
  if(tex_alone){
    paste0("\\documentclass{article} \n \\usepackage{booktabs} \n \\usepackage{graphicx} \n\\begin{document}\n",
           tab_intermed,
           "\n \\end{document}") -> tab_intermed}
  
  tab_intermed -> final_table
  
  return(final_table)
}
```







\documentclass{article}
\usepackage{booktabs}
\usepackage{graphicx}

\begin{document}


\include{table_null}

\include{table_alternative}

\include{table_boot_null}

\include{table_boot_alternative}

\end{document}













# No Bootstrap

## Null Hypothesis


### Sample Size against number of observations for different levels

This is 3.1a and 

```{r}
sum_tab %>% 
  filter(hypothesis == "null" & bootstrap == FALSE & dist == "norm") %>% 
  
  filter(test.lev %in% c(0.01, 0.05) & 
           nreg == 5 & ar == 0 & p_alpha %in% c(0.01,0.05)) %>% 
  
  select(sample, rej, p_alpha, nreg, test.lev) %>% 
  arrange(p_alpha, sample) %>% 
  pivot_wider(id_cols = c(sample, nreg, test.lev),
              names_from = c(p_alpha), values_from = rej) %>% 
  arrange(test.lev, sample) %>% 
  
  select(-test.lev) %>% 
  kable(format = "latex",
        digits = 3,
        col.names = c("n", "# Regressors", "0.01", "0.05"), 
        booktabs = TRUE) %>% 
  kable_styling(full_width = FALSE) %>% 
  kable_paper() %>% 
  #pack_rows("Normal Distribution",1, 10) %>%
  #pack_rows("$t_3$ Distribution", 11, 20) %>% 
  
  add_header_above(c(" " = 2, "$\\\\gamma_c$" = 2),escape = FALSE) %>% 
  #add_header_above(c(" " = 2, "Normal Distr." = 2), escape = FALSE) %>% 
  
  pack_rows("Level 0.01",1, 5) %>%
  pack_rows("Level 0.05", 6, 10) -> tab1

```

### Sample Size against number of observations for different number of coefficients

```{r}
sum_tab %>% 
  filter(hypothesis == "null" & bootstrap == FALSE & dist == "norm") %>% 
  
  filter(test.lev == 0.05 & nreg %in% c(1,5,10) & ar == 0 & p_alpha == 0.05) %>% 
  
  select(sample, rej, p_alpha, test.lev, nreg) %>% 
  arrange(p_alpha) %>% 
  pivot_wider(id_cols = c(sample, test.lev, p_alpha),
              names_from = c(nreg), values_from = rej) %>% 
  
  kable(format = "latex", 
        digits = 3,
        col.names = c("n", "Level","$\\gamma_c$", "1","5","10"), 
        booktabs = TRUE, escape = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  kable_paper() %>% 
  
  add_header_above(c(" " = 3, "# Regressors" = 3)) -> tab2
```


### Autoregressive Behaviour

```{r}
sum_tab %>% 
  filter(hypothesis == "null" & bootstrap == FALSE & dist == "norm") %>% 
  
  filter(test.lev == 0.05 & nreg==5 & ar %in% c(0,1,0.5)& p_alpha == 0.05) %>% 
  
  select(sample, rej, p_alpha, ar, test.lev, nreg) %>% 
  arrange(ar) %>% 
  pivot_wider(id_cols = c(sample, test.lev, p_alpha, nreg),
              names_from = c(ar), values_from = rej) %>% 
  
  kable(format = "latex", booktabs = TRUE,
        digits = 3,
        col.names = c("n", "Level","$\\gamma_c$",
                      "\\# Regressors", "0","0.5","1"),  escape = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  kable_paper() %>% 
  
  add_header_above(c(" " = 4, "$\\\\rho$" = 3), escape = FALSE)  -> tab3 

# pack_rows("Normal Distribution",1, 5) %>%
# pack_rows("$t_3$ Distribution", 6, 10, escape = FALSE)  -> tab3 
```


### Save First Tables for Null no BS

```{r}

column_tables(list(tab1), 
              caption = paste0("Simulation performance of the asymptotic test under the null of no distortion. Data for a Normal Distribution identical to Figure \\ref{fig_out_sim_null} left panel."), 
              label = "fig_out_sim_null_tableft") %>% 
  paste(., 
        
        column_tables(list(tab2), 
                      caption = paste0("Simulation performance of the asymptotic test under the null of no distortion. Data for a Normal Distribution identical to Figure \\ref{fig_out_sim_null} middle panel."), 
                      label = "fig_out_sim_null_tabmid"), sep = "\n") %>% 
  
  paste(., 
        column_tables(list(tab3), 
                      caption = paste0("Simulation performance of the asymptotic test under the null of no distortion. Data for a Normal Distribution identical to Figure \\ref{fig_out_sim_null} right panel."), 
                      label = "fig_out_sim_null_tabright"), sep = "\n") %>% 
  
  cat(file = here("data-raw/text/v8/","table_null.tex"))
```


## Alternative


```{r}
plot_specs_overall %>% 
  filter(bootstrap==FALSE & hypothesis=="alternative") %>% 
  distinct(out_prop, p_alpha, ar,nreg) -> plot_specs

table_list_alt <- ""

plot_specs %>% 
  mutate(text = "Simulation performance under the alternative for varying sample sizes and outlier magnitudes for a Normal Distribution when the dependent variable is a  ", 
         text = paste0(text, case_when(ar == 0 ~"cross-sectional process", 
                                       ar == 0.5 ~"stationary autoregressive process with coefficient of 0.5 on the autoregressive term", 
                                       ar == 1 ~"unit-root process"))) %>% 
  
  mutate(text = paste0(text, " and ", 
                       case_when(out_prop == 0.10 ~ "10\\% of the sample is outlier-contaminated.", 
                                 out_prop == 0.15 ~ "15\\% of the sample is outlier-contaminated."))) %>% 
  
  mutate(text = paste0(text, " Estimation was carried out with ",
                       nreg, " regressor",ifelse(nreg>1,"s",""),".")) %>% 
  
  pull(text) -> alt_caption_list


alt_label_list <- paste0("simluation_alternative_table_",1:nrow(plot_specs))
```


```{r}
table_list_alt <- ""
for(i in 1:nrow(plot_specs) ){
  
  print(paste("AR:",plot_specs[i,"ar"], 
              "NREG:", plot_specs[i,"nreg"], 
              "Outl. Prop:", plot_specs[i,"out_prop"], sep = " "))
  
  sum_tab %>% 
    filter(hypothesis == "alternative" & bootstrap == FALSE & dist == "norm") %>% 
    filter(test.lev == 0.01 & p_alpha == 0.05) %>% 
    filter(out_prop == plot_specs[i,"out_prop"] & 
             nreg == plot_specs[i,"nreg"] & 
             ar == plot_specs[i,"ar"]) -> datalt
  
  datalt %>% 
    select(sample, ar, rej, out_prop, test.lev, p_alpha, nreg, lambda) %>% 
    pivot_wider(id_cols = c(sample, ar, out_prop, test.lev, p_alpha, nreg),
                names_from = c(lambda), values_from = c(rej)) -> df_to_table
  
  df_to_table %>% 
    kable(format = "latex", 
          booktabs = TRUE,
          escape = FALSE,
          digits = 3,
          col.names = c("n","$\\rho$", "Outl. Prop.", "Level",
                        "$\\gamma_c$","\\# Regressors", "2","3","4","6")) %>% 
    kable_styling(full_width = FALSE) %>% 
    kable_paper() %>%  
    
    add_header_above(header = c(" " = 6, 
                                "Rejection Frequency for $\\\\lambda$" = 4), 
                     escape = FALSE) -> tab_intermed
  
  
  column_tables(list(tab_intermed), 
                caption = alt_caption_list[i], 
                label = alt_label_list[i], resize = TRUE) %>% 
    
    paste0(table_list_alt, ., sep = "\n") -> table_list_alt
  
}
```


```{r}
#  paste0("\\documentclass{article} \n \\usepackage{booktabs} \n \\usepackage{graphicx} \n\\begin{document}\n",
#            table_list_alt,
#            "\n \\end{document}") %>% 
# cat(file = here("data-raw/text/v8/table_alternative.tex"))


cat(table_list_alt,file = here("data-raw/text/v8/table_alternative.tex"))
```



# Bootstrap

test.lev==0.05 & p_alpha==0.05 & nreg==5 & ar==0 & dist == "norm" &
clean.sample == TRUE & boot.pval.scale == 1

## Null

```{r}
datnull <- sum_tab[sum_tab$bootstrap==TRUE&sum_tab$hypothesis=="null",]
datnull <- datnull[datnull$test.lev==0.05,]


datnull %>% 
  select(dist, sample, clean.sample, nreg, ar, test.lev, p_alpha, 
         boot.pval.scale, 
         rej, rej.L1.boot, rej.L2.boot) %>% 
  arrange(dist, sample) %>% 
  mutate(clean.sample = ifelse(clean.sample, "Cleaned","Raw")) %>% 
  
  pivot_wider(id_cols = c(dist, sample, nreg, ar, test.lev, p_alpha),
              names_from = c(clean.sample, boot.pval.scale),
              values_from = c(rej, rej.L1.boot, rej.L2.boot)) %>% 
  
  select(dist:p_alpha, 
         # asym
         rej_Cleaned_1, 
         # raw
         rej.L1.boot_Raw_1, 
         rej.L2.boot_Raw_1, 
         # cleaned
         rej.L1.boot_Cleaned_1, 
         rej.L2.boot_Cleaned_1, 
         # cleaned scaled
         rej.L1.boot_Cleaned_5, 
         rej.L2.boot_Cleaned_5) %>% 
  mutate(across( c(contains("rej")) , ~format(round(.,3),nsmall = 3))) %>% 
  
  select(-dist) %>% 
  kable(
    format = "latex", booktabs = TRUE, 
    col.names = c("n","\\# Regressors", "$\\rho$", "Level","$\\gamma_c$"," ",
                  rep(c("$L_1$","$L_2$"),3)), 
    escape = FALSE
  ) %>% 
  kable_paper() %>% 
  add_header_above(c(" " = 5, "Asymp." = 1,  "Raw" = 2, "Clean" = 2, "Clean Scaled" = 2)) %>% 
  add_header_above(c(" " = 5, "Rejection Frequency" = 7)) %>% 
  
  pack_rows("Normal Distribution",1, 4) %>%
  pack_rows("$t_3$ Distribution", 5, 8, escape = FALSE) -> tab_boot_null
```



```{r}
column_tables(list(tab_boot_null), 
              caption = "Simulation performance of the bootstrap tests under the null of no distortion when the reference distribution does and does not match the error distribution in the DGP. \\vspace{0.1cm}", 
              label = "fig_boot_sim_null_table", resize = TRUE) -> tab_boot_null


cat(tab_boot_null, file = here("data-raw/text/v8/table_boot_null.tex"))
```


## Alternative


```{r}
table_list_boot_alt <- ""
for(i in c(2,3, 4, 6)){
  
  sum_tab %>% 
    filter(bootstrap==TRUE, 
           hypothesis=="alternative",
           lambda == i) %>% 
    select(dist, lambda, sample, clean.sample, nreg, ar,
           test.lev, p_alpha, boot.pval.scale, rej, 
           rej.L1.boot, rej.L2.boot) %>% 
    arrange(dist, test.lev, sample) %>% 
    
    mutate(clean.sample = ifelse(clean.sample, "Cleaned","Raw")) %>% 
    
    pivot_wider(id_cols = c(dist, lambda, sample, nreg, ar, test.lev, p_alpha),
                names_from = c(clean.sample, boot.pval.scale),
                values_from = c(rej, rej.L1.boot, rej.L2.boot)) %>% 
    
    mutate(across( c(contains("rej")) , ~format(round(.,3),nsmall = 3))) %>% 
    
    select(dist:p_alpha, 
           # asym
           rej_Cleaned_1, 
           # raw
           rej.L1.boot_Raw_1, 
           rej.L2.boot_Raw_1, 
           # cleaned
           rej.L1.boot_Cleaned_1, 
           rej.L2.boot_Cleaned_1, 
           # cleaned scaled
           rej.L1.boot_Cleaned_5, 
           rej.L2.boot_Cleaned_5) %>% 
    
    select(-dist) %>% 
    kable(
      format = "latex", booktabs = TRUE, 
      col.names = c("$\\lambda$", "n","\\# Regressors", "$\\rho$", "Level","$\\gamma_c$"," ",
                    rep(c("$L_1$","$L_2$"),3)), 
      escape = FALSE
    ) %>% 
    kable_paper() %>% 
    add_header_above(c(" " = 6, "Asymp." = 1, "Raw" = 2, "Clean" = 2, "Clean Scaled" = 2)) %>% 
    add_header_above(c(" " = 6, "Rejection Frequency" = 7)) %>% 
    
    pack_rows("Normal Distribution",1, 8) %>%
    pack_rows("$t_3$ Distribution", 9, 16, escape = FALSE) -> tab_boot_alt_intermed
  
  
  column_tables(list(tab_boot_alt_intermed), 
                caption = paste("Simulation performance under the alternative for varying sample sizes when using the bootstrap implementations of our test (for outlier magnitude of ",i,"SD of the error term)."), 
                label = paste0("fig_out_sim_alt_boot_table",i), resize = TRUE) %>% 
    
    paste0(table_list_boot_alt, ., sep = "\n") -> table_list_boot_alt
  
}
```

```{r}
cat(table_list_boot_alt, file = here("data-raw/text/v8/table_boot_alternative.tex"))
```
