---
title: "getspanel: Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getspanel: Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

```{r setup}
library(getspanel)
```

Currently the package is called \texttt{getspanel} to align with the \texttt{gets} package, but it's main function of course remains the **isatpanel** function.

A quick overview over what has changed:

-   We can now use the function approach as well as the traditional gets approach. This means that we can specify a model using `y` and `mxreg` as well as `time` and `id` as vectors, but we can now also simply supply a `data.frame` and a `function` in the form `y ~ x + z + I(x^2)` to e.g. specify polynomials. This means we will then need an `index` argument, which specifies the

-   The `ar` argument now works

-   We can now use the `fixest` package to speed up model estimation with large `i` (for short panels, the default method is still faster).The package can be activated using the new `engine` argument.

-   Using the `fixest` package also allows us to calculate **clustered standard errors**.

-   We can now be certain that unbalanced panels would work as intended, which was not the case before.

-   The `mxbreak` and `break.method` arguments have been removed. Instead the function now produces the break matrix itself. This now implements the following saturation methods in a user friendly way:

    -   **iis**: Impulse Indicator Saturation
    -   **jsis**: **Joint** Step Indicator Saturation (Common Breaks over time)
    -   **csis**: **Coefficient** Step Indicator Saturation (Common Coefficient Breaks over time)
    -   **fesis**: **Fixed Effect** Step Indicator Saturation (Breaks in the Group Fixed Effect over time)
    -   **cfesis**: **Coefficient Fixed Effect** Step Indicator Saturation (Breaks in the coefficient for each individual)

# The isatpanel function

We first load the artificially created data.

```{r}
data("pandata_simulated")
head(pandata_simulated)
```

Let's go through the various cases.

```{r, eval= FALSE}
isatpanel(data = pandata_simulated,formula = gdp ~ temp, index = c("country","year"),effect = "twoways",ar = 1,fesis = TRUE)
```
